### 2024-10-16 README.Rmd
...

[<img src="vignettes/cols4all2.jpg" width="900"/>](vignettes/cols4all2.jpg)

@@

[<img src="vignettes/cols4all_fair_sort_cbf.jpg" width="900"/>](vignettes/cols4all_fair_sort_cbf.jpg)

@@

[<img src="vignettes/cols4all_div.jpg" width="900"/>](vignettes/cols4all_div.jpg)

@@

[<img src="vignettes/c4a_pals.jpg" width="900"/>](vignettes/c4a_pals.jpg)

@@

[<img src="vignettes/area7.jpg" width="900"/>](vignettes/area7.jpg)

@@

[<img src="vignettes/area7d.jpg" width="900"/>](vignettes/area7d.jpg)

@@

[<img src="vignettes/line7_wt.jpg" width="440"/>](vignettes/line7_wt.jpg)
[<img src="vignettes/line7_bk.jpg" width="440"/>](vignettes/line7_bk.jpg)

@@

[<img src="vignettes/friendly13.jpg" width="900"/>](vignettes/friendly13.jpg)

>>>>

[<img src="articles/cols4all2.jpg" width="900"/>](articles/cols4all2.jpg)

@@

[<img src="articles/cols4all_fair_sort_cbf.jpg" width="900"/>](articles/cols4all_fair_sort_cbf.jpg)

@@

[<img src="articles/cols4all_div.jpg" width="900"/>](articles/cols4all_div.jpg)

@@

[<img src="articles/c4a_pals.jpg" width="900"/>](articles/c4a_pals.jpg)

@@

[<img src="articles/area7.jpg" width="900"/>](articles/area7.jpg)

@@

[<img src="articles/area7d.jpg" width="900"/>](articles/area7d.jpg)

@@

[<img src="articles/line7_wt.jpg" width="440"/>](articles/line7_wt.jpg)
[<img src="articles/line7_bk.jpg" width="440"/>](articles/line7_bk.jpg)

@@

[<img src="articles/friendly13.jpg" width="900"/>](articles/friendly13.jpg)
